---
title: "Data Visualization Practice"
author: "Lew"
format: html
editor: visual
---

## 

```{r}
library(tidyverse)
library(here)
library(janitor)
```

```{r}
space_launches <- read_csv(here("data", "space_launches.csv"))
```

```{r}
space_launches_grouped <- space_launches |> 
  group_by(launch_year) |> 
  summarise(count = n())

space_launch_count <- space_launches |> 
  group_by(launch_year) %>%
  mutate(count_launches = n())

ggplot(data = space_launches_grouped, aes(x = launch_year, y = count)) +
  geom_path(aes(color = count), size = 29) + 
  coord_polar() +
  theme(panel.background = element_rect(fill = "green", color = "orange"),
        panel.grid.major = element_line(color = "red", size = 4),
        text = element_text(size = 12),
        axis.title = element_text(color = "Purple"),
        axis.text = element_text(color = "orange"),
        title = element_text(family = "Comic Sans MS")) +
  labs(x = "LAUNCH YEAR", y = "NUMBER OF LAUNCHES", title = "As evident from this chart, launches spiraled out of control from 1967 to 2017") +
  annotate("text",
           x = 0.1,
           y = 0.2,
           label = "lubridate",
           color = "blue", 
           size = 23)
  
```

```{r}
ggsave(here("docs", "uggo_plot.png"))
```

1.  Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by sector_general

2.  Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by year and commodity type

3.  Create a subset of the data that only contains observations from 2005 on, only for observations where `Sector_Detail2` contains the pattern \"PG&E\", then limit to columns `Calendar_Year`, `Sector_Detail2` and `Emissions_mtCO2e`.

```{r}
emissions <- read_csv(here("data", "San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv"))

#1
emissions %>%
  group_by(Sector_General) %>%
  summarise(total_emmisions = sum(Emissions_mtCO2e, na.rm = TRUE))

#2
emissions |> 
  group_by(Calendar_Year, Commodity_Type) |> 
  summarise(total_emissions = sum(Emissions_mtCO2e, na.rm = TRUE))
  
#3
emissions |> 
  filter(Calendar_Year >= 2005,
         str_detect(string = Sector_Detail2, pattern = "PG&E")) |> 
  select(Calendar_Year, Sector_Detail2, Emissions_mtCO2e)
  
```

Create a finalized graph (as perfect as you can make it) using the San Francisco GHG emissions dataset. **You** get to choose what you want to visualize. You can pick which variables & observations you\'re interested in. You may want to do some wrangling / summarizing first.

Once you\'ve decided on what to plot, create the best graph that you can to communicate what\'s going on with the data.

**Once you\'re done, drop your best graph (as a .png or .jpg) into the course Slack channel.**

```{r}
test <- emissions |> 
  group_by(Calendar_Year, Sector_General) |> 
  summarise(total_co2 = sum(Emissions_mtCO2e))
```

```{r}
ggplot(data = test, aes(x = Calendar_Year, y = total_co2)) + 
  geom_line(aes(color = Sector_General)) +
  theme_minimal() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank()) +
  labs(x = "Year",
       y = "Total CO2 emmisions (in megatons)",
       title = "Buildings and Transportation Have Accounted for the Majority of CO2 emissions in San Francisco since 1990",
       col = "General Sector")
  
ggsave(here("data", "emissions_graph.png"))
```
